---
title: "RPart2_Homework"
author: "NYC Data Science Academy"
output: html_document
---
## Question #1	

Each new term in the Fibonacci sequence is generated by adding the previous two terms. Starting with 1 and 2, the first 10 Fibonacci numbers are:

1, 2, 3, 5, 8, 13, 21, 34, 55, 89,...

Consider all the Fibonacci numbers whose values do not exceed four million. Find the sum of even-valued terms among them.

```{r Question 1}
fib <- function(x, y) {
  s <- x + y
  c(s, if (s < 4000000) fib(y, s))
}

f <- fib(0, 1)
sum(f[f %% 2 == 0])

## src: https://stackoverflow.com/questions/48566319/fibonacci-sequence-in-r
```

## Question #2

Write your own code to implement the multiplication between a matrix and a vector. In case you forget it, here's the definition of matrix multiplication. For an m?n matrix A and an n-dimensional vector x, y = Ax is an m-dimensional vector, where 
\begin{align}y[i] = \sum_{j=1}^nA[i,j]x[j] \text{ for } i = 1,2,3,...m\end{align}

```{r Question 2}
Ax = matrix(c(1:9), ncol = 3, nrow = 3)
x = c(1:3)
y = numeric(nrow(Ax))

matrix_mult <- function(mat, vec){
  
  row_c = nrow(mat)
  res = numeric(row_c)
  
  for(i in 1:row_c){
    res[i] = sum(mat[i, ]*vec);
  }
  
  return(res)
}

matrix_mult(Ax, x)

```


## Question #3:

Write a function that calculates the median absolute deviation (MAD) of a numeric vector. The median absolute deviation is a robust alternative to standard deviation as a measure of dispersion. For vector X, it is defined as  
$$MAD = median(|X_i-median(X)|)$$
```{r Question 3}
x = c(1, 1, 2, 2, 4, 6, 9)
md = c()
for(i in 1:length(x)){
  md[i] = median(abs(x[i]-median(x)))
}
mad = median(md)
mad
```


## Question #4: 

Suppose we have a  character vector as follows: `Names <- "John Andrew Thomas"`
Write some R code to obtain the following output:

\begin{align}\text{"John@gmail.com; Andrew@gmail.com; Thomas@gmail.com"}\end{align}

```{r Question 4}
names <- "John Andrew Thomas"
name_single = strsplit(names, ' ')[[1]]
tmp = c()
for(i in 1:length(name_single)){
  n = paste(gsub(" ", "", name_single[i]), c("@gmail.com"), sep = "")
  tmp[i] = n
}

paste0(tmp[1:3], collapse = "; ")
```

## Question #5:

Write R code to generate a vector with the following elements, **without using loops**.

"aa" "ba" "ca" "da" "ea" "ab" "bb" "cb" "db" "eb" "ac" "bc" "cc" "dc" "ec" "ad" "bd" "cd" "dd" "ed" "ae" "be" "ce" "de" "ee"

```{r Question 5}
a = c('a','b','c','d','e')
b = sort(rep(a,5))
c = paste0(a,b)
c
```

## Question #6:

Write an R function named `compare` which takes two words as arguments/inputs and returns "Equal Length" if the number of characters are equal in two words and "Not Equal Length" otherwise. It should work as following: 
```
>>compare("EPS568","Summer") 
"Equal Length"					
>>compare("EPS568","SummerA") 
"Not Equal Length"
```
```{r Question 6}
compare <- function(x, y){
  a = nchar(x)
  b = nchar(y)
  
  ifelse(a == b, "Equal Length", "Not Equal Length")
}

compare("1111", "2222")
```

## Challenge Question:

The game of craps is played as follows:

* Roll two six-sided dice; let x be the sum of the dice on the first roll.
* If x is 7 or 11, you automatically win.
* If x is 2, 3 or 12, you lose.
* If x is any other value (4, 5, 6, 8, 9, 10), x is then called the "point". Continue to re-roll the dice until you either roll the "point" again or a 7. 
    + If you obtain the established point x again, you win.
    + If a 7 is rolled before the point, you lose.


1. Write an R function to play this game once all the way through. You can use the expression 
`x <- sum(sample(1:6, 2, replace=T))` 
to simulate the sum of two rolled dice. The outcome of this expression should be a character element of either "Win" or "Loss".

2. Now, use the R expression you develop in (1), and repeat this game 1000 times hypothetically using a *for loop*. You should save the result of 1000 games in a vector with each element is either "Win" or "Loss". 

```{r Challenge Question}

```





